Equations & R Code

### 2017-01-02 manuscript/coexistence-stability_SI.Rmd
adds ELE reference formatting

---
layout: 12pt
header-includes:
  - \usepackage{lineno}
  - \linenumbers
  - \usepackage{setspace}
  - \usepackage{todonotes}
  - \onehalfspacing
  - \usepackage{rotating}
  - \usepackage{color, soul}
  - \usepackage[font={small},labelfont={sf,bf},labelsep=space]{caption}
  - \usepackage{tikz}
bibliography: ~/Dropbox/Bibliography/CoexistStability.bib
csl: components/ecology.csl

>>>>

---
layout: 12pt
header-includes:
  - \usepackage{lineno}
  - \linenumbers
  - \usepackage{setspace}
  - \usepackage{todonotes}
  - \onehalfspacing
  - \usepackage{rotating}
  - \usepackage{color, soul}
  - \usepackage[font={small},labelfont={sf,bf},labelsep=space]{caption}
  - \usepackage{tikz}
bibliography: ~/Dropbox/Bibliography/CoexistStability.bib
csl: components/ecology_letters.csl

### 2017-01-02 manuscript/coexistence-stability_ms.Rmd
adds ELE reference formatting

---
layout: 12pt
header-includes:
  - \usepackage{lineno}
  - \linenumbers
  - \usepackage{setspace}
  - \usepackage{todonotes}
  - \doublespacing
  - \usepackage{rotating}
  - \usepackage{color, soul}
  - \usepackage[font={footnotesize},labelfont={sf,bf},labelsep=space]{caption}
  - \usepackage{sectsty}
bibliography: ~/Dropbox/Bibliography/CoexistStability.bib
csl: components/ecology.csl

>>>>

---
layout: 12pt
header-includes:
  - \usepackage{lineno}
  - \linenumbers
  - \usepackage{setspace}
  - \usepackage{todonotes}
  - \doublespacing
  - \usepackage{rotating}
  - \usepackage{color, soul}
  - \usepackage[font={footnotesize},labelfont={sf,bf},labelsep=space]{caption}
  - \usepackage{sectsty}
bibliography: ~/Dropbox/Bibliography/CoexistStability.bib
csl: components/ecology_letters.csl

### 2017-01-02 manuscript/coexistence-stability_ms.tex
adds ELE reference formatting

MacArthur (1955), Elton (1958), and even Darwin (Turnbull et al. 2013)
recognized the potential for compensatory dynamics among species to
stabilize ecosystem functioning in fluctuating environments. This idea
underlies the ``insurance hypothesis'' (Yachi and Loreau 1999), which
suggests ecosystem variability decreases with diversity because species
respond dissimilarly to environmental variation, broadening the range of
conditions under which the community maintains function (Loreau 2010). A
variety of theoretical models all predict a negative relationship
between species richness and ecosystem variability (Lehman and Tilman
2000, Ives and Hughes 2002, Loreau and {{de Mazancourt}} 2013), and
experimental tests tend to support such a prediction (Tilman et al.
2006, Hector et al. 2010).

However, the ability of biodiversity-ecosystem functioning (BEF)
experiments to accurately represent real-world dynamics is debated
(Wardle 2016, Eisenhauer et al. 2016). Much of the debate centers around
the fact that BEF experimental protocols do not allow species gains to
offset species losses. Theoretical work on diversity-variability
relationships typically suffers from the same limitation: it recognizes
the role of environmental variability in driving population fluctuations
which destabilize ecosystems, but ignores the potential for
environmental variability to promote species richness and thereby help
stabilize ecosystems (Loreau 2010, but see Chesson et al. 2001).

Fluctuating environmental conditions are an important ingredient for
stable species coexistence, both in theoretical models (Chesson 2000a,
Chesson et al. 2004) and in natural communities (C{á}ceres 1997,
Descamps-Julien and Gonzalez 2005, Adler et al. 2006, Angert et al.
2009). Such ``fluctuation-dependent'' coexistence requires that species
have unique environmental responses and that environmental conditions
vary so that each species in a community experiences favorable and
unfavorable conditions, which prevents competitive exclusion (Chesson
2000a). When coexistence is maintained by a fluctuation-dependent
mechanism, an increase in environmental variability might lead to an
increase in species richness and, consequently, a decrease in ecosystem
variability. However, increasing environmental variability may also
increase ecosystem variability by increasing the fluctuations of
individual species, regardless of species richness. These countervailing
effects of environmental variability present an interesting paradox:
while increasing environmental variability should increase ecosystem
variability, that increase might be offset by an increase in richness.
Such a paradox complicates predictions about how ecosystems will respond
to predicted departures from historical ranges of environmental
variability.

The opposing effects of environmental variability on ecosystem
variability might explain the mixed results from empirical studies on
the diversity-variability relationship. Observational tests of the
diversity-variability relationship, which require sampling across
natural diversity gradients, have yielded negative (Hautier et al.
2014), neutral (Valone and Hoffman 2003, Cusson et al. 2015), and
positive (Sasaki and Lauenroth 2011) relationships. In a meta-analysis
of diversity-variability relationships based on observational studies in
terrestrial ecosystems, Jiang and Pu (2009) found no significant
evidence for an effect of species richness on ecosystem variability.
\tc{blue}{This may be because environmental variability varies across natural diversity gradients, affecting both richness and ecosystem variability.}
The idiosyncratic results of these empirical studies contrast with the
consistent conclusions from theoretical work that ignores feedbacks
between variability and richness.

The gap between theoretical expectations and empirical results of
richness-variability relationships might reflect the divergence of
theory developed to explain species coexistence and theory developed to
explain diversity and ecosystem variability. One reason these two
disciplines have diverged is because they have focused on different
questions. Diversity-variability studies typically ask how ecosystem
variability responds to different levels of species richness at a given
level of environmental variability (reviewed in Kinzig et al. 2001,
Loreau 2010), whereas coexistence studies ask how species richness
responds to different levels of environmental variability (Chesson and
Warner 1981).

@@

We developed a semi-discrete consumer-resource model that allows many
species to coexist on one resource by either the storage effect or
relative nonlinearity. In our model, the consumer can be in one of
two-states: a dormant state \(D\) and a live state \(N\). The dormant
state could represent, for example, the seed bank of an annual plant.
Transitions between \(N\) and \(D\) occur at discrete intervals \(\tau\)
with continuous-time consumer-resource dynamics between discrete
transitions. Thus, our model is formulated as ``pulsed differential
equations'' (Pachepsky et al. 2008, Mailleret and Lemesle 2009, Mordecai
et al. 2016). For clarity we refer to \(\tau\) as years and the growing
time between years as seasons with daily (\(t\)) time steps.

@@

For example, in Fig. 1C we show two species' resource uptake curves that
are relatively nonlinear. Species B has the lowest \(R^*\) and would
competitively exclude species A in the absence of environmental
fluctuations. But, fluctuating resource supplies can benefit species A
because it can take advantage of relatively high resource levels due its
higher saturation point. Stable coexistence is only possible, however,
if each species creates a disadvantage for itself when abundant. This
occurs in our model because when a resource conservative species (e.g.,
species B in Fig. 1C) is abundant, resource levels will remain high for
a longer period of time after a pulse because its draw down of resources
saturates. Likewise, when a resource acquisitive species (e.g., species
A in Fig. 1C) is abundant, it quickly draws down resources to levels
that favor resource conservative species. Such reciprocity ensures
species can increase when rare and stabilizes coexistence (Armstrong and
McGehee 1980, Chesson 2000a, Chesson et al. 2004).

@@

Our results may explain why deviations from the negative
diversity-variability relationship often come from observational studies
(Jiang and Pu 2009). Observational studies must rely on natural
diversity gradients, which do not control for differences in
environmental variability among sites. If species richness depends on
environmental variability, it is entirely possible to observe positive
diversity-variability relationships. For example, Sasaki and Lauenroth
(2011) found a positive relationship between species richness and the
temporal variability of plant abundance in a semi-arid grassland. Their
data came from a six sites that were 6 km apart. While Sasaki and
Lauenroth explained their results in terms of dominant species' effects,
it is also possible that each site experienced sufficiently different
levels of environmental variability to influence species coexistence.
DeClerck et al. (2006) also found a positive diversity-variability when
sampling conifer richness and the variability of productivity across a
large spatial gradient in the Sierra Nevada.

@@

Second, whether local fluctuation-dependent communities can receive the
benefit of additional species depends on a diverse regional species
pool. If the regional pool is not greater in size than the local species
pool, than ecosystem variability will increase with environmental
variability in a similar manner as in fluctuation-independent
communities because species richness will be fixed (Fig. 5A,B).
Metacommunity theory has made clear the importance of rescue effects to
avoid species extinctions (Brown and Kodric-Brown 1997, Leibold et al.
2004). Here, instead of local immigration by a resident species working
to rescue a species from extinction, immigration to the local community
by a new species rescues ecosystem processes from becoming more variable
(Fig. 5C,D). Thus, our results reinforce the importance of both local
and regional biodiversity conservation. Just as declines in local
species richness can destabilize ecosystem functioning (Tilman et al.
2006, Hector et al. 2010, Hautier et al. 2014), species losses at larger
spatial scales can also increase ecosystem variability. Wang and Loreau
(2014) show that regional ecosystem variability depends on regional
biodiversity through its effects on beta diversity and, in turn, the
asynchrony of functioning in local communities. Our results show that,
when coexistence is fluctuation-dependent, regional biodiversity
declines could also affect local ecosystem functioning by limiting local
colonization events that could be possible under scenarios of increasing
environmental variability (Fig. 5).

@@

Adler, P. B., J. HilleRisLambers, P. C. Kyriakidis, Q. Guan, and J. M.
Levine. 2006. Climate variability has a stabilizing effect on the
coexistence of prairie grasses. Proceedings of the National Academy of
Sciences 103:12793--12798.

Angert, A. L., T. E. Huxman, P. Chesson, and D. L. Venable. 2009.
Functional tradeoffs determine species coexistence via the storage
effect. Proceedings of the National Academy of Sciences of the United
States of America 106:11641--11645.

Armstrong, R. A., and R. McGehee. 1980. Competitive Exclusion. The
American Naturalist 115:151--170.

Brown, J. H., and A. Kodric-Brown. 1997. Turnover Rates in Insular
Biogeography : Effect of Immigration on Extinction. Ecology 58:445--449.

C{á}ceres, C. E. 1997. Temporal variation, dormancy, and coexistence: a
field test of the storage effect. Proceedings of the National Academy of
Sciences 94:9171--9175.

Chesson, P. 2000a. Mechanisms of Maintenance of Species Diversity.
Annual Review of Ecology and Systematics 31:343--366.

Chesson, P. 2000b. General theory of competitive coexistence in
spatially-varying environments. Theoretical population biology
58:211--37.

Chesson, P. L. 1994. Multispecies Competition in Variable Environments.
Theoretical Population Biology 45:227.

Chesson, P. L., and R. R. Warner. 1981. Environmental Variability
Promotes Coexistence in Lottery Competitive Systems. The American
Naturalist 117:923--943.

Chesson, P., R. L. E. Gebauer, S. Schwinning, N. Huntly, K. Wiegand, M.
S. K. Ernest, A. Sher, A. Novoplansky, and J. F. Weltzin. 2004. Resource
pulses, species interactions, and diversity maintenance in arid and
semi-arid environments. Oecologia 141:236--253.

Chesson, P., S. W. Pacala, and C. Neuhauser. 2001. Environmental Niches
and Ecosystem Functioning. Pages 213--245 \emph{in} A. P. Kinzig, S. W.
Pacala, and D. Tilman, editors. The functional consequences of
biodiversity: Empirical progress and theoretical extensions. Princeton
University Press, Princeton.

Cusson, M., T. P. Crowe, R. Ara{ú}jo, F. Arenas, R. Aspden, F. Bulleri,
D. Davoult, K. Dyson, S. Fraschetti, K. Herk{ü}l, C. Hubas, S. Jenkins,
J. Kotta, P. Kraufvelin, A. Mign{é}, M. Molis, O. Mulholland, L. M.-L.
No{ë}l, D. M. Paterson, J. Saunders, P. J. Somerfield, I. Sousa-Pinto,
N. Spilmont, A. Terlizzi, and L. Benedetti-Cecchi. 2015. Relationships
between biodiversity and the stability of marine ecosystems: Comparisons
at a European scale using meta-analysis. Journal of Sea Research
98:5--14.

DeClerck, F. A. J., M. G. Barbour, and J. O. Sawyer. 2006. Species
richness and stand stability in conifer forests of the Sierra Nevada.
Ecology 87:2787--2799.

Descamps-Julien, B., and A. Gonzalez. 2005. Stable coexistence in a
fluctuating environment: An experimental demonstration. Ecology
86:2815--2824.

Eisenhauer, N., A. D. Barnes, S. Cesarz, D. Craven, O. Ferlian, F.
Gottschall, J. Hines, A. Sendek, J. Siebert, M. P. Thakur, and M.
T{ü}rke. 2016. Biodiversity-ecosystem function experiments reveal the
mechanisms underlying the consequences of biodiversity change in real
world ecosystems. Journal of Vegetation Science 27:1061--1070.

Elton, C. 1958. The Ecology of Invasions by Animals and Plants. Pages
1689--1699. University of Chicago Press, Chicago.

Hautier, Y., E. W. Seabloom, E. T. Borer, P. B. Adler, W. S. Harpole, H.
Hillebrand, E. M. Lind, A. S. MacDougall, C. J. Stevens, J. D. Bakker,
Y. M. Buckley, C. Chu, S. L. Collins, P. Daleo, E. I. Damschen, K. F.
Davies, P. a Fay, J. Firn, D. S. Gruner, V. L. Jin, J. a Klein, J. M. H.
Knops, K. J. {La Pierre}, W. Li, R. L. McCulley, B. a Melbourne, J. L.
Moore, L. R. O'Halloran, S. M. Prober, A. C. Risch, M. Sankaran, M.
Schuetz, and A. Hector. 2014. Eutrophication weakens stabilizing effects
of diversity in natural grasslands. Nature 508:521--5.

Hector, A., Y. Hautier, P. Saner, L.Wacker, R. Bagchi, J. Joshi, M.
Scherer-Lorenzen, E. M. Spehn, E. Bazeley-White, M.Weilenmann, M. C.
Caldeira, P. G. Dimitrakopoulos, J. a. Finn, K. Huss-Danell, A.
Jumpponen, and M. Loreau. 2010. General stabilizing effects of plant
diversity on grassland productivity through population asynchrony and
overyielding. Ecology 91:2213--2220.

Ives, A. R., and J. B. Hughes. 2002. General relationships between
species diversity and stability in competitive systems. The American
naturalist 159:388--395.

Jiang, L., and Z. Pu. 2009. Different effects of species diversity on
temporal stability in single-trophic and multitrophic communities. The
American Naturalist 174:651--659.

Kinzig, A. P., S. W. Pacala, and D. Tilman (Eds.). 2001. The functional
consequences of biodiversity: Empirical progress and theoretical
extensions. Pages i--365. Princeton University Press, Princeton.

Lehman, C. L., and D. Tilman. 2000. Biodiversity, Stability, and
Productivity in Competitive Communities. The American Naturalist
156:534--552.

Leibold, M. A., M. Holyoak, N. Mouquet, P. Amarasekare, J. M. Chase, M.
F. Hoopes, R. D. Holt, J. B. Shurin, R. Law, D. Tilman, M. Loreau, and
A. Gonzalez. 2004. The metacommunity concept: A framework for
multi-scale community ecology.

Loreau, M. 1998. Biodiversity and ecosystem functioning: a mechanistic
model. Proceedings of the National Academy of Sciences of the United
States of America 95:5632--5636.

Loreau, M. 2010. From Polutations to Ecosystems: Theoretical Fondations
for a New Ecological Synthesis.

Loreau, M., and C. {{de Mazancourt}}. 2013. Biodiversity and ecosystem
stability: A synthesis of underlying mechanisms. Ecology Letters
16:106--115.

MacArthur, R. 1955. Fluctuations of Animal Populations and a Measure of
Community Stability. Ecology 36:533--536.

Mailleret, L., and V. Lemesle. 2009. A note on semi-discrete modelling
in the life sciences. Philosophical transactions. Series A,
Mathematical, physical, and engineering sciences 367:4779--4799.

Mordecai, E. A., K. Gross, and C. E. Mitchell. 2016. Within-Host Niche
Differences and Fitness Trade-offs Promote Coexistence of Plant Viruses.
The American Naturalist 187:E13--E26.

Pachepsky, E., R. M. Nisbet, and W. W. Murdoch. 2008. Between discrete
and continuous: Consumer-resource dynamics with synchronized
reproduction. Ecology 89:280--288.

Sasaki, T., and W. K. Lauenroth. 2011. Dominant species, rather than
diversity, regulates temporal stability of plant communities. Oecologia
166:761--768.

Soetaert, K., T. Petzoldt, and R. W. Setzer. 2010. Package deSolve :
Solving Initial Value Differential Equations in R. Journal Of
Statistical Software 33:1--25.

Team, R. 2013. R Development Core Team. R: A Language and Environment
for Statistical Computing.

Tilman, D. 1982. Resource competition and community structure. Pages
1--296.

Tilman, D., P. B. Reich, and J. M. H. Knops. 2006. Biodiversity and
ecosystem stability in a decade-long grassland experiment. Nature
441:629--632.

Turnbull, L. A., J. M. Levine, M. Loreau, and A. Hector. 2013.
Coexistence, niches and biodiversity effects on ecosystem functioning.
Ecology Letters 16:116--127.

Valone, T. J., and C. D. Hoffman. 2003. A mechanistic examination of
diversity-stability relationships in annual plant communities. Oikos
103:519--527.

Wang, S., and M. Loreau. 2014. Ecosystem stability in space: \(\alpha\),
\(\beta\) and \(\gamma\) variability. Ecology Letters 17:891--901.

Wardle, D. A. 2016. Do experiments exploring plant diversity-ecosystem
functioning relationships inform how biodiversity loss impacts natural
ecosystems? Journal of Vegetation Science 27:646--653.

Yachi, S., and M. Loreau. 1999. Biodiversity and ecosystem productivity
in a fluctuating environment: the insurance hypothesis. Proceedings of
the National Academy of Sciences of the United States of America
96:1463--1468.

>>>>

MacArthur (1955), Elton (1958), and even Darwin (Turnbull et al. 2013)
recognized the potential for compensatory dynamics among species to
stabilize ecosystem functioning in fluctuating environments. This idea
underlies the ``insurance hypothesis'' (Yachi \& Loreau 1999), which
suggests ecosystem variability decreases with diversity because species
respond dissimilarly to environmental variation, broadening the range of
conditions under which the community maintains function (Loreau 2010). A
variety of theoretical models all predict a negative relationship
between species richness and ecosystem variability (Lehman \& Tilman
2000; Ives \& Hughes 2002; Loreau \& {{de Mazancourt}} 2013), and
experimental tests tend to support such a prediction (Tilman et al.
2006; Hector et al. 2010).

However, the ability of biodiversity-ecosystem functioning (BEF)
experiments to accurately represent real-world dynamics is debated
(Eisenhauer et al. 2016; Wardle 2016). Much of the debate centers around
the fact that BEF experimental protocols do not allow species gains to
offset species losses. Theoretical work on diversity-variability
relationships typically suffers from the same limitation: it recognizes
the role of environmental variability in driving population fluctuations
which destabilize ecosystems, but ignores the potential for
environmental variability to promote species richness and thereby help
stabilize ecosystems (Loreau 2010, but see Chesson et al. 2001).

Fluctuating environmental conditions are an important ingredient for
stable species coexistence, both in theoretical models (Chesson 2000a;
Chesson et al. 2004) and in natural communities (C{á}ceres 1997;
Descamps-Julien \& Gonzalez 2005; Adler et al. 2006; Angert et al.
2009). Such ``fluctuation-dependent'' coexistence requires that species
have unique environmental responses and that environmental conditions
vary so that each species in a community experiences favorable and
unfavorable conditions, which prevents competitive exclusion (Chesson
2000a). When coexistence is maintained by a fluctuation-dependent
mechanism, an increase in environmental variability might lead to an
increase in species richness and, consequently, a decrease in ecosystem
variability. However, increasing environmental variability may also
increase ecosystem variability by increasing the fluctuations of
individual species, regardless of species richness. These countervailing
effects of environmental variability present an interesting paradox:
while increasing environmental variability should increase ecosystem
variability, that increase might be offset by an increase in richness.
Such a paradox complicates predictions about how ecosystems will respond
to predicted departures from historical ranges of environmental
variability.

The opposing effects of environmental variability on ecosystem
variability might explain the mixed results from empirical studies on
the diversity-variability relationship. Observational tests of the
diversity-variability relationship, which require sampling across
natural diversity gradients, have yielded negative (Hautier et al.
2014), neutral (Valone \& Hoffman 2003; Cusson et al. 2015), and
positive (Sasaki \& Lauenroth 2011) relationships. In a meta-analysis of
diversity-variability relationships based on observational studies in
terrestrial ecosystems, Jiang \& Pu (2009) found no significant evidence
for an effect of species richness on ecosystem variability.
\tc{blue}{This may be because environmental variability varies across natural diversity gradients, affecting both richness and ecosystem variability.}
The idiosyncratic results of these empirical studies contrast with the
consistent conclusions from theoretical work that ignores feedbacks
between variability and richness.

The gap between theoretical expectations and empirical results of
richness-variability relationships might reflect the divergence of
theory developed to explain species coexistence and theory developed to
explain diversity and ecosystem variability. One reason these two
disciplines have diverged is because they have focused on different
questions. Diversity-variability studies typically ask how ecosystem
variability responds to different levels of species richness at a given
level of environmental variability (reviewed in Kinzig et al. 2001;
Loreau 2010), whereas coexistence studies ask how species richness
responds to different levels of environmental variability (Chesson \&
Warner 1981).

@@

We developed a semi-discrete consumer-resource model that allows many
species to coexist on one resource by either the storage effect or
relative nonlinearity. In our model, the consumer can be in one of
two-states: a dormant state \(D\) and a live state \(N\). The dormant
state could represent, for example, the seed bank of an annual plant.
Transitions between \(N\) and \(D\) occur at discrete intervals \(\tau\)
with continuous-time consumer-resource dynamics between discrete
transitions. Thus, our model is formulated as ``pulsed differential
equations'' (Pachepsky et al. 2008; Mailleret \& Lemesle 2009; Mordecai
et al. 2016). For clarity we refer to \(\tau\) as years and the growing
time between years as seasons with daily (\(t\)) time steps.

@@

For example, in Fig. 1C we show two species' resource uptake curves that
are relatively nonlinear. Species B has the lowest \(R^*\) and would
competitively exclude species A in the absence of environmental
fluctuations. But, fluctuating resource supplies can benefit species A
because it can take advantage of relatively high resource levels due its
higher saturation point. Stable coexistence is only possible, however,
if each species creates a disadvantage for itself when abundant. This
occurs in our model because when a resource conservative species (e.g.,
species B in Fig. 1C) is abundant, resource levels will remain high for
a longer period of time after a pulse because its draw down of resources
saturates. Likewise, when a resource acquisitive species (e.g., species
A in Fig. 1C) is abundant, it quickly draws down resources to levels
that favor resource conservative species. Such reciprocity ensures
species can increase when rare and stabilizes coexistence (Armstrong \&
McGehee 1980; Chesson 2000a; Chesson et al. 2004).

@@

Our results may explain why deviations from the negative
diversity-variability relationship often come from observational studies
(Jiang \& Pu 2009). Observational studies must rely on natural diversity
gradients, which do not control for differences in environmental
variability among sites. If species richness depends on environmental
variability, it is entirely possible to observe positive
diversity-variability relationships. For example, Sasaki and Lauenroth
(2011) found a positive relationship between species richness and the
temporal variability of plant abundance in a semi-arid grassland. Their
data came from a six sites that were 6 km apart. While Sasaki and
Lauenroth explained their results in terms of dominant species' effects,
it is also possible that each site experienced sufficiently different
levels of environmental variability to influence species coexistence.
DeClerck et al. (2006) also found a positive diversity-variability when
sampling conifer richness and the variability of productivity across a
large spatial gradient in the Sierra Nevada.

@@

Second, whether local fluctuation-dependent communities can receive the
benefit of additional species depends on a diverse regional species
pool. If the regional pool is not greater in size than the local species
pool, than ecosystem variability will increase with environmental
variability in a similar manner as in fluctuation-independent
communities because species richness will be fixed (Fig. 5A,B).
Metacommunity theory has made clear the importance of rescue effects to
avoid species extinctions (Brown \& Kodric-Brown 1997; Leibold et al.
2004). Here, instead of local immigration by a resident species working
to rescue a species from extinction, immigration to the local community
by a new species rescues ecosystem processes from becoming more variable
(Fig. 5C,D). Thus, our results reinforce the importance of both local
and regional biodiversity conservation. Just as declines in local
species richness can destabilize ecosystem functioning (Tilman et al.
2006; Hector et al. 2010; Hautier et al. 2014), species losses at larger
spatial scales can also increase ecosystem variability. Wang \& Loreau
(2014) show that regional ecosystem variability depends on regional
biodiversity through its effects on beta diversity and, in turn, the
asynchrony of functioning in local communities. Our results show that,
when coexistence is fluctuation-dependent, regional biodiversity
declines could also affect local ecosystem functioning by limiting local
colonization events that could be possible under scenarios of increasing
environmental variability (Fig. 5).

@@

Adler, P.B., HilleRisLambers, J., Kyriakidis, P.C., Guan, Q. \& Levine,
J.M. (2006). Climate variability has a stabilizing effect on the
coexistence of prairie grasses. \emph{Proceedings of the National
Academy of Sciences}, 103, 12793--12798.

Angert, A.L., Huxman, T.E., Chesson, P. \& Venable, D.L. (2009).
Functional tradeoffs determine species coexistence via the storage
effect. \emph{Proceedings of the National Academy of Sciences of the
United States of America}, 106, 11641--11645.

Armstrong, R.A. \& McGehee, R. (1980). Competitive Exclusion. \emph{The
American Naturalist}, 115, 151--170.

Brown, J.H. \& Kodric-Brown, A. (1997). Turnover Rates in Insular
Biogeography : Effect of Immigration on Extinction. \emph{Ecology}, 58,
445--449.

C{á}ceres, C.E. (1997). Temporal variation, dormancy, and coexistence: a
field test of the storage effect. \emph{Proceedings of the National
Academy of Sciences}, 94, 9171--9175.

Chesson, P. (2000a). Mechanisms of Maintenance of Species Diversity.
\emph{Annual Review of Ecology and Systematics}, 31, 343--366.

Chesson, P. (2000b). General theory of competitive coexistence in
spatially-varying environments. \emph{Theoretical population biology},
58, 211--37.

Chesson, P., Gebauer, R.L.E., Schwinning, S., Huntly, N., Wiegand, K.,
Ernest, M.S.K., et al. (2004). Resource pulses, species interactions,
and diversity maintenance in arid and semi-arid environments.
\emph{Oecologia}, 141, 236--253.

Chesson, P., Pacala, S.W. \& Neuhauser, C. (2001). Environmental Niches
and Ecosystem Functioning. In: \emph{The functional consequences of
biodiversity: Empirical progress and theoretical extensions} (eds.
Kinzig, A.P., Pacala, S.W. \& Tilman, D.). Princeton University Press,
Princeton, pp. 213--245.

Chesson, P.L. (1994). Multispecies Competition in Variable Environments.
\emph{Theoretical Population Biology}, 45, 227.

Chesson, P.L. \& Warner, R.R. (1981). Environmental Variability Promotes
Coexistence in Lottery Competitive Systems. \emph{The American
Naturalist}, 117, 923--943.

Cusson, M., Crowe, T.P., Ara{ú}jo, R., Arenas, F., Aspden, R., Bulleri,
F., et al. (2015). Relationships between biodiversity and the stability
of marine ecosystems: Comparisons at a European scale using
meta-analysis. \emph{Journal of Sea Research}, 98, 5--14.

DeClerck, F.A.J., Barbour, M.G. \& Sawyer, J.O. (2006). Species richness
and stand stability in conifer forests of the Sierra Nevada.
\emph{Ecology}, 87, 2787--2799.

Descamps-Julien, B. \& Gonzalez, A. (2005). Stable coexistence in a
fluctuating environment: An experimental demonstration. \emph{Ecology},
86, 2815--2824.

Eisenhauer, N., Barnes, A.D., Cesarz, S., Craven, D., Ferlian, O.,
Gottschall, F., et al. (2016). Biodiversity-ecosystem function
experiments reveal the mechanisms underlying the consequences of
biodiversity change in real world ecosystems. \emph{Journal of
Vegetation Science}, 27, 1061--1070.

Elton, C. (1958). \emph{The Ecology of Invasions by Animals and Plants}.
University of Chicago Press, Chicago.

Hautier, Y., Seabloom, E.W., Borer, E.T., Adler, P.B., Harpole, W.S.,
Hillebrand, H., et al. (2014). Eutrophication weakens stabilizing
effects of diversity in natural grasslands. \emph{Nature}, 508, 521--5.

Hector, A., Hautier, Y., Saner, P., L.Wacker, Bagchi, R., Joshi, J., et
al. (2010). General stabilizing effects of plant diversity on grassland
productivity through population asynchrony and overyielding.
\emph{Ecology}, 91, 2213--2220.

Ives, A.R. \& Hughes, J.B. (2002). General relationships between species
diversity and stability in competitive systems. \emph{The American
naturalist}, 159, 388--395.

Jiang, L. \& Pu, Z. (2009). Different effects of species diversity on
temporal stability in single-trophic and multitrophic communities.
\emph{The American Naturalist}, 174, 651--659.

Kinzig, A.P., Pacala, S.W. \& Tilman, D. (Eds.). (2001). \emph{The
functional consequences of biodiversity: Empirical progress and
theoretical extensions}. Princeton University Press, Princeton.

Lehman, C.L. \& Tilman, D. (2000). Biodiversity, Stability, and
Productivity in Competitive Communities. \emph{The American Naturalist},
156, 534--552.

Leibold, M.A., Holyoak, M., Mouquet, N., Amarasekare, P., Chase, J.M.,
Hoopes, M.F., et al. (2004). The metacommunity concept: A framework for
multi-scale community ecology. \emph{Ecology letters}.

Loreau, M. (1998). Biodiversity and ecosystem functioning: a mechanistic
model. \emph{Proceedings of the National Academy of Sciences of the
United States of America}, 95, 5632--5636.

Loreau, M. (2010). \emph{From Polutations to Ecosystems: Theoretical
Fondations for a New Ecological Synthesis}.

Loreau, M. \& {{de Mazancourt}}, C. (2013). Biodiversity and ecosystem
stability: A synthesis of underlying mechanisms. \emph{Ecology Letters},
16, 106--115.

MacArthur, R. (1955). Fluctuations of Animal Populations and a Measure
of Community Stability. \emph{Ecology}, 36, 533--536.

Mailleret, L. \& Lemesle, V. (2009). A note on semi-discrete modelling
in the life sciences. \emph{Philosophical transactions. Series A,
Mathematical, physical, and engineering sciences}, 367, 4779--4799.

Mordecai, E.A., Gross, K. \& Mitchell, C.E. (2016). Within-Host Niche
Differences and Fitness Trade-offs Promote Coexistence of Plant Viruses.
\emph{The American Naturalist}, 187, E13--E26.

Pachepsky, E., Nisbet, R.M. \& Murdoch, W.W. (2008). Between discrete
and continuous: Consumer-resource dynamics with synchronized
reproduction. \emph{Ecology}, 89, 280--288.

Sasaki, T. \& Lauenroth, W.K. (2011). Dominant species, rather than
diversity, regulates temporal stability of plant communities.
\emph{Oecologia}, 166, 761--768.

Soetaert, K., Petzoldt, T. \& Setzer, R.W. (2010). Package deSolve :
Solving Initial Value Differential Equations in R. \emph{Journal Of
Statistical Software}, 33, 1--25.

Team, R. (2013). R Development Core Team. \emph{R: A Language and
Environment for Statistical Computing}.

Tilman, D. (1982). \emph{Resource competition and community structure.}

Tilman, D., Reich, P.B. \& Knops, J.M.H. (2006). Biodiversity and
ecosystem stability in a decade-long grassland experiment.
\emph{Nature}, 441, 629--632.

Turnbull, L.A., Levine, J.M., Loreau, M. \& Hector, A. (2013).
Coexistence, niches and biodiversity effects on ecosystem functioning.
\emph{Ecology Letters}, 16, 116--127.

Valone, T.J. \& Hoffman, C.D. (2003). A mechanistic examination of
diversity-stability relationships in annual plant communities.
\emph{Oikos}, 103, 519--527.

Wang, S. \& Loreau, M. (2014). Ecosystem stability in space: \(\alpha\),
\(\beta\) and \(\gamma\) variability. \emph{Ecology Letters}, 17,
891--901.

Wardle, D.A. (2016). Do experiments exploring plant diversity-ecosystem
functioning relationships inform how biodiversity loss impacts natural
ecosystems? \emph{Journal of Vegetation Science}, 27, 646--653.

Yachi, S. \& Loreau, M. (1999). Biodiversity and ecosystem productivity
in a fluctuating environment: the insurance hypothesis.
\emph{Proceedings of the National Academy of Sciences of the United
States of America}, 96, 1463--1468.
